SimSurvey demo

### 2021-12-15 tutorial/tutorial.Rmd
Wrap-up complete draft of tutorial

@@

## Simulate population
set.seed(271)
pop <- sim_abundance(ages = seq(1, 10), years = seq(1, 20)) %>%
  sim_distribution(grid = make_grid(res = c(10, 10), depth_range = c(10, 500)),
                   ays_covar = sim_ays_covar(phi_age = 0.8, phi_year = 0.2),
                   depth_par = sim_parabola(mu = 200, sigma = 30))

@@

## Expand grid data for predictions
grid_dat <- as_tibble(select(pop$grid_xy, x, y, depth)) %>% distinct()
grid_dat <- purrr::map_dfr(sort(unique(dat$year)), ~ bind_cols(grid_dat, year = .))
grid_dat$offset <- mean(dat$offset)

@@

>>>>

- Fit a geostatistical using [sdmTMB](https://github.com/pbs-assess/sdmTMB) using survey data simulated using [SimSurvey](https://github.com/PaulRegular/SimSurvey)

@@

## Simulate population
set.seed(17)
pop <- sim_abundance(ages = seq(1, 10), years = seq(1, 15)) %>%
  sim_distribution(grid = make_grid(res = c(10, 10), depth_range = c(10, 500)),
                   ays_covar = sim_ays_covar(phi_age = 0.8, phi_year = 0.2),
                   depth_par = sim_parabola(mu = 200, sigma = 30))

@@

## Expand grid data for predictions
grid_dat <- as_tibble(select(survey$grid_xy, x, y, depth)) %>% distinct()
grid_dat <- purrr::map_dfr(sort(unique(dat$year)), ~ bind_cols(grid_dat, year = .))
grid_dat$offset <- mean(dat$offset)

@@

## What if?

- With these tools we can test whether a model can fill in holes in a survey caused by problems (e.g., vessel issues) or changing protocol (e.g., restricted areas)
- In the example below, strata 5 and 6 are excluded following year 10 and the analyses run in the previous section are re-run using the affected survey data

```{r what-if, exercise = TRUE, exercise.eval = TRUE}

## Simulate population
set.seed(17)
pop <- sim_abundance(ages = seq(1, 10), years = seq(1, 15)) %>%
  sim_distribution(grid = make_grid(res = c(10, 10), depth_range = c(10, 500)),
                   ays_covar = sim_ays_covar(phi_age = 0.8, phi_year = 0.2),
                   depth_par = sim_parabola(mu = 200, sigma = 30))

## Simulate survey data
survey <- sim_survey(pop, n_sims = 1)

## DROP DATA FROM STRATA 5 AND 6 FOLLOWING YEAR 10
survey$setdet <- filter(survey$setdet, !(year > 10 & strat %in% 5:6))

## Run stratified analysis with missing areas
survey <- survey %>% run_strat()

## Expand grid data for predictions
grid_dat <- as_tibble(select(survey$grid_xy, x, y, depth)) %>% distinct()
grid_dat <- purrr::map_dfr(sort(unique(dat$year)), ~ bind_cols(grid_dat, year = .))
grid_dat$offset <- mean(dat$offset)

## Conclusion

- Surveys are expensive and complex and we want to make the most of the data we obtain
- [SimSurvey](https://github.com/PaulRegular/SimSurvey) offers a means of simulating some of the complexities
- Design-based analyses are elegant and efficient and work best when everything is standard
- Problem is that surveys change and this is where model-based approaches may be more powerful
- [sdmTMB](https://github.com/pbs-assess/sdmTMB) facilitates fast fitting of powerful geostatistical models
